Synthesizing Symmetric Lenses

### 2018-07-09 papers/SymmetricLenses/main.tex
stuff

>>>>

More broadly, information theory and probabilistic languages are common tools
in natural language understanding,  machine translation, information retrieval,
data extraction and grammatical inference (see Pereira~\cite{pereira:info-theory},
for an introduction).  Indeed, our work was inspired, in part, by the PADS format
inference tool~\cite{pads:synthesis}, which was in turn inspired by earlier work on
probabilistic gramatical inference
and information extraction~\cite{kushmerick-thesis,arasu:extracting}.  More specifically, PADS
used an information-theoretic metric to help judge the quality of inferred grammars
for ad hoc data formats.  However, PADS did not synthesize data transformers, and
we are not aware of the use of information-theoretic principles in type-directed or syntax-guided
synthesis of DSL programs.
